### 2014-11-09 store-opsem.tex
All proofs added

% First, we prove few useful lemmas:

% \begin{lemma}[]
% \end{lemma}

@@

For every well-formed execution state $\E$, and contract class $\tau 
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, If:

@@

      Lemma~\ref{lem:auxred-wf}. Goal (\romannumeral 2) is the

@@

      Since local state (i.e., $\Theta(r)$) is causally consistent
      (lemma~\ref{lem:local-state-is-cc}) using $H10$ and $H12$ we
      derive the following:

@@

          \item SSCase L: Hypothesis is
          \begin{smathpar}
          \begin{array}{cr}
             {\sf hbo'}(a,c) \wedge \Rso'(c,\eff)& H\npp\\
          \end{array}
          \end{smathpar}
          Inverting $H31$:
          \begin{smathpar}
          \begin{array}{cr}
             {\sf hbo'}(a,c)& H\npp\\
             \Rso'(c,\eff)& H\npp\\
          \end{array}
          \end{smathpar}
          From $H33$ and $H16$, we infer:
          \begin{smathpar}
          \begin{array}{cr}
            c \in \Theta(r) & H\npp \\
          \end{array}
          \end{smathpar}
          Since local state is causally consistent
          (lemma~\ref{lem:local-state-is-cc}), from $H32$ and $H34$,
          we have:
          \begin{smathpar}
          \begin{array}{cr}
            a \in \Theta(r) & H\npp\\
          \end{array}
          \end{smathpar}
           Proof follows from $H35$ and $H18$.
        % End of SSCase
        \end{itemize}
      % End of SCases
      \end{itemize}

    \item Case \rulelabel{SC}: Hypotheses:
      \begin{smathpar}
      \begin{array}{cr}
        \tau = {\sf StronglyConsistent} & H\npp \\
        \auxred{\Theta} {(\E,\langle s,i,op \rangle)} {r}
        {(\E',\eff)} & H\npp\\ 
        \E.A \subseteq \Theta(r) & H\npp\\
        \dom(\Theta') = \dom(\Theta) & H\npp\\
        \forall r'\in \dom(\Theta'). \Theta'(r') = \Theta(r') \cup
          \{\eff\} & H\npp\\
      \end{array}
      \end{smathpar}
      Let $\EffSoup' = \E'.\EffSoup$, $\Rvis' = \E'.\Rvis$, $\Rso' =
      \E'.\Rso$, and $\hboZ' =(\Rso' \cup \Rvis')^{+}$. Inversion on
      $H37$ gives: 
      \begin{smathpar}
      \begin{array}{cr}
        \EffSoup' = \EffSoup \cup \{\eff\} & H\npp\\
        \visZ' = \Theta(r)\times\eff ~\cup~ \visZ & H\npp\\
        \Rso' = \EffSoup_{{\sf SessID}=s,\,{\sf SeqNo}<i}\times\eff ~\cup~ \Rso & H\npp\\
        \sameobjZ' = \EffSoup' \times \EffSoup'& H\npp\\
      \end{array}
      \end{smathpar}
       Goal (\romannumeral 1) follows from $H36$ and
       Lemma~\ref{lem:auxred-wf}. Expanding the definition of $\scc$,
       goal is the following:
      \begin{smathpar}
      \begin{array}{cr}
        \forall a.~\sameobj{a}{\eff} \Rightarrow \vis{a}{\eff} 
          ~\vee~ \vis{\eff}{a} ~\vee~ a = \eff & G\mpp\\
      \end{array}
      \end{smathpar}
      By similar reasoning as with the \rulelabel{EC} case,
      we get a context with following hypotheses:
      \begin{smathpar}
      \begin{array}{cr}
        a \in \EffSoup' & H\npp\\
        {\sameobjZ'(a,\eff)}  & H\npp\\
      \end{array}
      \end{smathpar}
      And the goal is the following:
      \begin{smathpar}
      \begin{array}{cr}
        \vis{a}{\eff} ~\vee~ \vis{\eff}{a} ~\vee~ a = \eff & G\mpp\\
      \end{array}
      \end{smathpar}
      From $H40$ and $H44$, we know that either $a \in \EffSoup$ or $a
      = \eff$. If $a = \eff$, then $G8$ follows trivially. On the
      other hand, when $a \in \EffSoup$, from $H37$ we know that $a
      \in \Theta(r)$. From $H41$, we derive:
      \begin{smathpar}
      \begin{array}{cr}
        a \in \visZ'(\eff)& \\
      \end{array}
      \end{smathpar}
      Which means first disjunct of $G8$ is valid, proving the
      theorem.
  % End of all cases    
  \end{itemize}

\end{proof}

\begin{corollary}[Soundness]
\label{thm:soundness}
For every well-formed execution state $\E$, and contract class $\tau
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, and for every consistency
contract $\cv$ in the contract class $\tau$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,op_\tau :: 
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i+1,\sigma \rangle \pll \Sigma)
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv[\eff/\cureff]$
\end{corollary}
\begin{proof}
Follows from Theorems~\ref{thm:classification-sound} and
\ref{thm:weak-soundness}
\qed
\end{proof}

>>>>

First, we prove a useful lemma:

\begin{lemma}[Auxiliary Reduction Preserves Well-Formedness]
For every well-formed execution state $\E$, if
$\auxred{\Theta}{(\E,\langle s,i,op \rangle)} {r} {(\E',\eff)}$, then
$\E'$ is well-formed.
\end{lemma}
\begin{proof}
  Let us denote $\E.\EffSoup$, $\E.\Rvis$, $\E.\Rso$, and $\E.\sameobjZ$
  as $\EffSoup$, $\Rvis$, $\Rso$, and $\sameobjZ$ respectively.
  Likewise, let us denote $\E'.\EffSoup$, $\E'.\Rvis$, $\E'.\Rso$, and
  $\E'.\sameobjZ$ as $\EffSoup$, $\Rvis$, $\Rso$, and $\sameobjZ$
  respectively. By inversion on $\auxred{\Theta}{(\E,\langle s,i,op
  \rangle)} {r} {(\E',\eff)}$, we have following hypotheses:
  \begin{smathpar}
  \begin{array}{cr}
    r \in \dom(\Theta) & H\npp\\
    ctxt = {\ctxtFn}^{*}(\Theta(r)) & H\npp\\
    \Ops(op)(ctxt) {\rdtredsto}^{*} v & H\npp\\
    \eff = (s,i,op,v) & H\npp\\
    \{\eff'\} = \EffSoup_{({\sf SessID}=s,\,{\sf SeqNo}=i-1)}\\
    \EffSoup' = \{\eff\} \cup \EffSoup & H\npp\\
    \visZ' = \Theta(r)\times\{\eff\} \cup \visZ & H\npp\\
    \soZ' = (\soZ^{-1}(\eff') \cup \eff') \times\{\eff\} \cup \soZ
      & H\npp \\
    \sameobjZ' = \EffSoup' \times \EffSoup' & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\E$ is well-formed, from the definition of
  well-formedness and \emph{models} relation, we have the following:
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a \in \EffSoup). \neg\hboZ(a,a) & H\npp\\
    \forall (a,b \in \EffSoup). \visZ(a,b) \Rightarrow 
      \sameobjZ(a,b) & H\npp\\
    \forall (a,b,c \in \EffSoup). \soZ(a,b) \conj \soZ(b,c) \Rightarrow
      \soZ(a,c) & H\npp\\
    \forall (a \in \EffSoup). \sameobjZ(a,a) & H\npp\\
    \forall (a,b \in \EffSoup). \sameobjZ(a,b) \Rightarrow 
      \sameobjZ(b,a) & H\npp\\
    \forall (a,b,c \in \EffSoup). \soZ(a,b) \conj \soZ(b,c) \Rightarrow
      \soZ(a,c) & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\hboZ = (\Rvis \cup \Rso)^{+}$, $H8$ is equivalent to
  conjunction of following assertions:
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a \in \EffSoup). \neg\visZ(a,a) & H\npp\\
    \forall (a \in \EffSoup). \neg\soZ(a,a) & H\npp\\
    \forall (a,b \in \EffSoup). \neg (\visZ(a,b) \conj \soZ(b,a)) & H\npp\\
  \end{array}
  \end{smathpar}
  Since $\eff$ is fresh, $\eff \notin \Theta(r)$. From $H4$, $H5$, and
  $H14$, we have the acyclicity property for $\visZ'$:
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a \in \EffSoup'). \neg\visZ'(a,a) & H\npp\\
  \end{array}
  \end{smathpar}
  Also, $\eff \notin \EffSoup$, and from $H4$, $H6$ and $H15$, we have
  acyclicity for $\soZ'$: 
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a \in \EffSoup'). \neg\soZ'(a,a) & H\npp\\
  \end{array}
  \end{smathpar}
  Similarly, from the uniqueness of $\eff$, and $H5$, $H6$, and $H16$,
  we have the following:
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a,b \in \EffSoup'). \neg (\visZ'(a,b) \conj \soZ'(b,a)) & H\npp\\
  \end{array}
  \end{smathpar}
  From $H17-19$, we prove the acyclicity of $\hboZ'$: 
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a \in \EffSoup').\neg\hboZ(a,a) & G\mpp\\
  \end{array}
  \end{smathpar}
  The $\sameobjZ'$ relation is simply the cross product
  $\EffSoup' \times \EffSoup'$. Hence following trivially hold:
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a,b \in \EffSoup'). \visZ'(a,b) \Rightarrow 
      \sameobjZ'(a,b) & G\mpp\\
    \forall (a \in \EffSoup'). \sameobjZ'(a,a) & G\mpp\\
    \forall (a,b \in \EffSoup'). \sameobjZ'(a,b) \Rightarrow 
      \sameobjZ'(b,a) & G\mpp\\
  \end{array}
  \end{smathpar}
  Finally, from $H4$, $H6$ and $H10$, we have transitivity for $\soZ'$:
  \begin{smathpar}
  \begin{array}{cr}
    \forall (a,b,c \in \EffSoup'). \soZ'(a,b) \conj \soZ'(b,c) \Rightarrow
      \soZ'(a,c) & G\mpp\\
  \end{array}
  \end{smathpar}
  Well-formedness of $\E'$ follows from $G0-4$.
\end{proof}

We now define causal consistency property of the store formally:

\begin{definition}
  A store $\Theta$ is said to be causally consistent under an execution
  $\E=\Exec$ if and only if:
  \begin{smathpar}
  \begin{array}{cr}
    \hspace*{-0.5in}\forall (r\in{\sf dom}(\Theta)). \forall (\eff \in
      \Theta(r)). & \\
    \hspace*{0.3in}\forall (a\in \EffSoup). \hbo{a}{\eff} \Rightarrow a 
      \in \Theta(r) & H\npp \\
  \end{array}
  \end{smathpar}
  Where, $\hboZ = (\Rvis \cup \Rso)^{+}$
\end{definition}

@@

For every well-formed execution state $\E$, for every store $\Theta$
that is causally consistent under $\E$, and for every contract class
$\tau \in \{{\sf ec},{\sf cc},{\sf sc}\}$, if:

@@

      lemma~\ref{lem:auxred-wf}. Goal (\romannumeral 2) is the

@@

      Since $a,b \neq \eff$, we have that $\hboZ'(a,b) \Rightarrow
      \hboZ(a,b)$.  Since $\Theta(r)$ is causally consistent under
      $\E$, using $H10$ and $H12$ we derive the following:

@@

          \item SSCase L: Hypothesis is
          \begin{smathpar}
          \begin{array}{cr}
             {\sf hbo'}(a,c) \wedge \Rso'(c,\eff)& H\npp\\
          \end{array}
          \end{smathpar}
          Inverting $H31$:
          \begin{smathpar}
          \begin{array}{cr}
             {\sf hbo'}(a,c)& H\npp\\
             \Rso'(c,\eff)& H\npp\\
          \end{array}
          \end{smathpar}
          From $H33$ and $H16$, we infer:
          \begin{smathpar}
          \begin{array}{cr}
            c \in \Theta(r) & H\npp \\
          \end{array}
          \end{smathpar}
          Since $a,c \neq \eff$, we know that $\hboZ'(a,c) \Rightarrow
          \hboZ(a,c)$.  Since $\Theta(r)$ is causally consistent under
          $\E$, using $H32$ and $H34$ we derive the following:
          \begin{smathpar}
          \begin{array}{cr}
            a \in \Theta(r) & H\npp\\
          \end{array}
          \end{smathpar}
           Proof follows from $H35$ and $H18$.
        % End of SSCase
        \end{itemize}
      % End of SCases
      \end{itemize}

    \item Case \rulelabel{SC}: Hypotheses:
      \begin{smathpar}
      \begin{array}{cr}
        \tau = {\sf StronglyConsistent} & H\npp \\
        \auxred{\Theta} {(\E,\langle s,i,op \rangle)} {r}
        {(\E',\eff)} & H\npp\\ 
        \E.A \subseteq \Theta(r) & H\npp\\
        \dom(\Theta') = \dom(\Theta) & H\npp\\
        \forall r'\in \dom(\Theta'). \Theta'(r') = \Theta(r') \cup
          \{\eff\} & H\npp\\
      \end{array}
      \end{smathpar}
      Let $\EffSoup' = \E'.\EffSoup$, $\Rvis' = \E'.\Rvis$, $\Rso' =
      \E'.\Rso$, and $\hboZ' =(\Rso' \cup \Rvis')^{+}$. Inversion on
      $H37$ gives: 
      \begin{smathpar}
      \begin{array}{cr}
        \EffSoup' = \EffSoup \cup \{\eff\} & H\npp\\
        \visZ' = \Theta(r)\times\eff ~\cup~ \visZ & H\npp\\
        \Rso' = \EffSoup_{{\sf SessID}=s,\,{\sf SeqNo}<i}\times\eff ~\cup~ \Rso & H\npp\\
        \sameobjZ' = \EffSoup' \times \EffSoup'& H\npp\\
      \end{array}
      \end{smathpar}
       Goal (\romannumeral 1) follows from $H36$ and
       Lemma~\ref{lem:auxred-wf}. Expanding the definition of $\scc$,
       goal is the following:
      \begin{smathpar}
      \begin{array}{cr}
        \forall a.~\sameobj{a}{\eff} \Rightarrow \vis{a}{\eff} 
          ~\vee~ \vis{\eff}{a} ~\vee~ a = \eff & G\mpp\\
      \end{array}
      \end{smathpar}
      By similar reasoning as with the \rulelabel{EC} case,
      we get a context with following hypotheses:
      \begin{smathpar}
      \begin{array}{cr}
        a \in \EffSoup' & H\npp\\
        {\sameobjZ'(a,\eff)}  & H\npp\\
      \end{array}
      \end{smathpar}
      And the goal is the following:
      \begin{smathpar}
      \begin{array}{cr}
        \vis{a}{\eff} ~\vee~ \vis{\eff}{a} ~\vee~ a = \eff & G\mpp\\
      \end{array}
      \end{smathpar}
      From $H40$ and $H44$, we know that either $a \in \EffSoup$ or $a
      = \eff$. If $a = \eff$, then $G8$ follows trivially. On the
      other hand, when $a \in \EffSoup$, from $H37$ we know that $a
      \in \Theta(r)$. From $H41$, we derive:
      \begin{smathpar}
      \begin{array}{cr}
        a \in \visZ'(\eff)& \\
      \end{array}
      \end{smathpar}
      Which means first disjunct of $G8$ is valid, proving the
      theorem.
  % End of all cases    
  \end{itemize}
\end{proof}

\begin{corollary}[Soundness]
  \label{thm:soundness}
  For every well-formed execution state $\E$, for every store $\Theta$
  that is causally consistent under $\E$, for every contract class $\tau
  \in \{{\sf ec},{\sf cc},{\sf sc}\}$, and for every consistency
  contract $\cv$ in the contract class $\tau$, If:
  \begin{smathpar}
  (\E, \Theta, \langle s,i,op_\tau :: 
  \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
  \langle s,i+1,\sigma \rangle \pll \Sigma)
  \end{smathpar}
  then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
  $\E' \models \cv[\eff/\cureff]$
\end{corollary}
\begin{proof}
  Follows from Theorems~\ref{thm:classification-sound} and
  \ref{thm:weak-soundness}
  \qed
\end{proof}

We now show that every configuration of the store that is reachable
via the reduction relation ($\xrightarrow{}$) is causally consistent.

\begin{lemma}[Causal Consistency Preservation]
  \label{lem:local-state-is-cc}
  For every well-formed execution state $\E$, and a store $\Theta$
  that is causally consistent under $\E$, if: 
  \begin{smathpar}
    (\E, \Theta, \langle s,i,op_\tau ::
    \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
    \langle s,i+1,\sigma \rangle \pll \Sigma)
  \end{smathpar}
  then $\Theta'$ is causally consistent under $\E'$.
\end{lemma}
\begin{proof}
  By case analysis on on:
  \begin{smathpar}
    (\E, \Theta, \langle s,i,op_\tau ::
    \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
    \langle s,i+1,\sigma \rangle \pll \Sigma)
  \end{smathpar}
  Cases:
  \begin{itemize}
    \item Case \rulelabel{EffVis}: Final execution state is same as
    the initial (i.e., $\E' = \E$). Therefore, we need to prove that
    new store configuration $\Theta$ is causally consistent under
    $\E=\Exec$. Hypotheses:
    \begin{smathpar}
    \begin{array}{cr}
      r \in {\sf ReplID} & H\npp \\
      \eff \in A & H\npp \\
      \eff \notin \Theta(r)& H\npp \\
      \E.\visZ^{-1}(\eff) \cup \E.\soZ^{-1}(\eff) \subseteq \Theta(r)
      & H\npp \\
      \Theta' = \Theta \cup [r \mapsto \{\eff\} \cup \Theta(r)] & H\npp \\
      \hspace*{-0.5in}\forall (r\in{\sf dom}(\Theta)). \forall (\eff \in
        \Theta(r)). & \\
      \hspace*{0.3in}\forall (a\in\EffSoup). \hbo{a}{\eff} \Rightarrow a \in \Theta(r) & H\npp \\
    \end{array}
    \end{smathpar}
    From $H4$ and $H5$, it suffices to prove:
    \begin{smathpar}
    \begin{array}{cr}
      \forall (a\in \EffSoup). \hbo{a}{\eff} 
        \Rightarrow a \in \Theta'(r) & G\mpp\\
    \end{array}
    \end{smathpar}
    After \emph{intros}, hypotheses:
    \begin{smathpar}
    \begin{array}{cr}
      a\in\EffSoup & H\npp\\
      \hbo{a}{\eff} & H\npp \\
    \end{array}
    \end{smathpar}
    Goal:
    \begin{smathpar}
    \begin{array}{cr}
      a \in \Theta'(r) & G\mpp \\
    \end{array}
    \end{smathpar}
    Inversion on $H7$ leads to two cases:
    \begin{itemize}
      \item SCase \emph{$a$ directly precedes $\eff$ }: Hypothesis:
      \begin{smathpar}
      \begin{array}{cr}
        (\Rvis \cup \Rso)(a,\eff) & H\npp\\
      \end{array}
      \end{smathpar}
      From $H3$ and $H8$, we conclude that $a \in \Theta'(r)$.

      \item SCase \emph{$a$ transitively precedes $\eff$}: Hypothesis:
      \begin{smathpar}
      \begin{array}{cr}
        \exists (c \in \EffSoup). \hbo{a}{c} \wedge (\Rvis \cup
        \Rso)(c,\eff) & H\npp \\
      \end{array}
      \end{smathpar}
      Inverting $H9$:
      \begin{smathpar}
      \begin{array}{cr}
        c \in A & H\npp \\
        \hbo{a}{c} & H\npp \\
        (\Rvis \cup \Rso)(c,\eff) & H\npp \\
      \end{array}
      \end{smathpar}
      From $H3$ and $H12$, we have:
      \begin{smathpar}
      \begin{array}{cr}
        c \in \Theta'(r) & H\npp\\
      \end{array}
      \end{smathpar}
      From $H5$, $H13$ and $H11$, we conclude that $a \in \Theta'(r)$.
    \end{itemize}

    \item Cases \rulelabel{EC} and \rulelabel{CC}: Store configuration
    ($\Theta$) remains unchanged. Proof trivial.

    \item Case \rulelabel{SC}: $\Sigma = \tuplee{s,\sigma} \pll
    \Sigma_1$. Hypotheses:
    \begin{smathpar}
    \begin{array}{cr}
      r \in {\sf ReplID} & H\npp \\
      {\sf Unavailable}(\cv) & H\npp \\
      \E_1;\Theta_1;\tuplee{s,op(v); \sigma} 
        \;\xhookrightarrow{\eff,r}\; 
      \E;\Theta_2;\tuplee{s,\sigma} & H\npp\\
      \E_1.A \subseteq \Theta_1(r) & H\npp\\
      \dom(\Theta) = \dom(\Theta_2) & H\npp\\
      \forall r'\in \dom(\Theta). \Theta(r') = \Theta_2(r') \cup
      \{\eff\} & H\npp\\
    \end{array}
    \end{smathpar}
    Inductive hypothesis:
    \begin{smathpar}
    \begin{array}{cr}
      \hspace*{-0.5in}\forall (r'\in{\sf dom}(\Theta_1)). \forall (\eff' \in
        \Theta_1(r')). & \\
      \hspace*{0.3in}\forall (a\in\E_1.A). \hbo{a}{\eff'} \Rightarrow a
        \in \Theta_1(r') & IH\npp \\
    \end{array}
    \end{smathpar}
    The goal:
    \begin{smathpar}
    \begin{array}{cr}
      \hspace*{-0.5in}\forall (r'\in{\sf dom}(\Theta)). \forall (\eff' \in
        \Theta(r')). & \\
      \hspace*{0.3in}\forall (a\in\E.A). \hbo{a}{\eff'} \Rightarrow a
        \in \Theta(r') & G\mpp \\
    \end{array}
    \end{smathpar}
    Inverting $H16$:
    \begin{smathpar}
    \begin{array}{cr}
        \E.\EffSoup = \E_1.\EffSoup \cup \{\eff\} & H\npp\\
        \E.\visZ = \Theta_1(r)\times \{\eff\} ~\cup~ \E_1.\visZ & H\npp\\
        \E.\Rso = \E_1.\EffSoup_{{\sf SessID}=s,\,{\sf SeqNo}<i}\times
          \{\eff\} ~\cup~ \E_1.\Rso & H\npp\\
        \Theta_2 = \Theta_1 & H\npp\\
    \end{array}
    \end{smathpar}
    Using $H24$ to rewrite $H19$:
    \begin{smathpar}
    \begin{array}{cr}
      \forall r'\in \dom(\Theta). \Theta(r') = \Theta_1(r') \cup
      \{\eff\} & H\npp\\
    \end{array}
    \end{smathpar}
    Using $H25$ and $IH20$, we can reduce the goal ($G2$) to:
    \begin{smathpar}
    \begin{array}{cr}
      \forall (r'\in{\sf dom}(\Theta)). 
      \forall (a\in\E.\EffSoup). \hbo{a}{\eff} \Rightarrow a
        \in \Theta(r') & G\mpp \\
    \end{array}
    \end{smathpar}
    After \emph{intros}, hypotheses:
    \begin{smathpar}
    \begin{array}{cr}
      r' \in \dom(\Theta) & H\npp \\
      a \in \E.\EffSoup & H\npp\\
      \hbo{a}{\eff} & H\npp\\
    \end{array}
    \end{smathpar}
    Goal:
    \begin{smathpar}
    \begin{array}{cr}
      a \in \Theta(r) & G\mpp \\
    \end{array}
    \end{smathpar}
    From $H27$ and $H21$, we know that either $a \in \E_1.\EffSoup$ or
    $a = \eff$.
    \begin{itemize}
      \item If $a \in \E_1.\EffSoup$, then from $H17$, we know that $a
      \in \Theta_1(r)$. However, from $H25$ we know that $\Theta_1(r)
      \subset \Theta(r)$, which lets us conclude that $a \in
      \Theta(r)$.

      \item If $a = \eta$, then $H28$ is $\hbo{\eff}{\eff}$, which is
      $false$ since {\sf hbo} is irreflexive.
      \emph{ex\_falso\_quodlibet}.
    \end{itemize}
  % End of main cases  
  \end{itemize}
\qed
\end{proof}
